---
title: "GSS challange More Data"
author: "Kathleen Castro"
date: "03/14/2023"
output: html_document
---







```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~race + cappun ,data=mydata)
barchartGC(~race + cappun ,data=mydata)
```
  
According to this graph, it shows how the white favor the capital punishment while the black opposes it the most. 

## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```
  
Looking at the data provided above, we see that the whites have a 65% in favor of capital punishment while black carries a 57% of opposing it. Now looking at the second table we can also see that the whites carry an 80% of favoring capital punishment while "other" carries a 10.51 % opposing it.

## Now with More data



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfy the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
  
The difference between the two race types is on a very large level. Around 1300 white people favor while only 191 black people are in favor. This amount has a large gap between the two opposing races. When it comes to opposing the Capital Offense, 35.93 black people oppose while 10.93 white people oppose. 

```{r}
fisherXY (mydata$race,mydata$cappun, printAll=TRUE)
```

Now taking the fisherXY gives more data where we can see that each race, statistically, carries a different opinion where the t-text ends up being significant.

## More data version


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
In conclusion, we can confirm that more white people are in favor of the capital punishment while more black people are against it. The bar graph gives us the comparison of favors and oppositions between all three races. It shows how the white people have a higher bar in favor compared to the other two races. When looking at the second graph we see the comparison of two similar tables showing the percentage of votes for each race. The amount of whites compared to the other two races have a large difference in between ranging almost 20% under whites percentage which is at 80% in favor. The final graph shows the amount of votes between all three races where the whites carry the most votes in favor compared to the other races.

